---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# datools

The goal of datools is to cover a lot of convenient tools useful for machine learning consulting using R

# Build status

| Test    | Status     |
|---------|------------|
| Travis  | [![Build Status](https://travis-ci.org/DoktorMike/datools.svg?branch=master)](https://travis-ci.org/DoktorMike/datools)           |
| Codecov | [![Coverage Status](https://img.shields.io/codecov/c/github/DoktorMike/datools/master.svg)](https://codecov.io/github/DoktorMike/datools?branch=master)           |
| Wercker | [![wercker status](https://app.wercker.com/status/82dcdeafb5fae145580366ca3f95fc6d/s/master "wercker status")](https://app.wercker.com/project/byKey/82dcdeafb5fae145580366ca3f95fc6d) |
| Lifecycle | [![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing) |

## Installation

You can install datools from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("DoktorMike/datools")
```

## Example

Say you have a vector of weekdays and you would really like to have that one hot encoded for use in your algorithms then oneHotEncoder comes to the rescue!

```{r example}
## basic example code
library(datools)
library(lubridate)
oneHotEncoder(x=wday(seq(as.Date("2017-10-07"), by ="days", length.out = 10), 
                     label = TRUE))
```

## PCA fun

```{r pcaplot, echo=TRUE, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
library(datools)
data(iris)
plotPCAComponent(iris[,-5], iris$Species) + theme_minimal()
```

